### 2012-10-19 trunk/htdocs/references.tex
Expanded porous media section
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@1792 40876441-3496-0410-a613-a2fca35b2ae2

@@

>>>>

\bibitem{batchelor}
G.K. Batchelor
\textit{An Introduction to Fluid Mechanics},
Cambridge University Press (1967).

\bibitem{blake}
J.R. Blake, A spherical envelope approach to ciliary propusion,
\textit{J. Fluid Mech.}, \textbf{46}, 199, 1971.

@@

\bibitem{lighthill}
M.J. Lighthill,
On the squirming motion of nearly spherical deformable bodies through
liquid at very small Reynolds numbers,
\textit{Comm. Pure Appl. Math.}, \textbf{5}, 109, 1952.

\bibitem{isaac}
I. Llopis Fust\'e,
\textit{Hydrodynamic cooperativity in micro-swimmer suspensions},
Ph.D. Thesis, University of Barcelona, 2008.
